Details of specific functions

### 2018-02-23 inst/gitbook/03_specific-tutorials.Rmd
Revert "v0.5.1"
gitbook updates

Level | Name | Description | Source | 
------|------|---------------------------------------------------|--------|
2 | `ancestral.dist` | The distance between an element and its ancestor | `dispRity` |
2 | `centroids`<sup>1</sup> | The distance between each element and the centroid of the ordinated space | `dispRity` |
1 | `convhull.surface` | The surface of the convex hull formed by all the elements | [`geometry`](https://cran.r-project.org/web/packages/geometry/index.html)`::convhulln` |
1 | `convhull.volume` | The volume of the convex hull formed by all the elements | [`geometry`](https://cran.r-project.org/web/packages/geometry/index.html)`::convhulln` |
1 | `diagonal` | The longest distance in the ordinated space (like the diagonal in two dimensions) | `dispRity` |
1 | `ellipse.volume`<sup>1</sup> | The volume of the ellipsoid of the space | Donohue _et al._ (2013) |
1 | `mode.val` | The modal value | `dispRity` |
1 | `n.ball.volume` | The hyper-spherical (*n*-ball) volume | `dispRity` |
2 | `pairwise.dist` | The pairwise distances between elements | [`stats`](https://cran.r-project.org/web/packages/stats/index.html)`::dist` |
2 | `radius` | The radius of each dimensions | `dispRity` |
2 | `ranges` | The range of each dimension | `dispRity` |
1 | `span.tree.length` | The minimal spanning tree length | [`vegan`](https://cran.r-project.org/web/packages/vegan/index.html)`::spantree` |
2 | `variances` | The variance of each dimension | `dispRity` |

@@

The convex hull functions make a (good) estimation of the multidimensional properties of the ordinated space.

@@

The pairwise distances uses the function `stats::dist` and can take the normal `dist` options:

@@

>>>>

Level | Name | Description | Source | 
------|------|---------------------------------------------------|--------|
2 | `ancestral.dist` | The distance between an element and its ancestor | `dispRity` |
2 | `centroids`<sup>1</sup> | The distance between each element and the centroid of the ordinated space | `dispRity` |
1 | `convhull.surface` | The surface of the convex hull formed by all the elements | [`geometry`](https://cran.r-project.org/web/packages/geometry/index.html)`::convhulln$area` |
1 | `convhull.volume` | The volume of the convex hull formed by all the elements | [`geometry`](https://cran.r-project.org/web/packages/geometry/index.html)`::convhulln$vol` |
1 | `diagonal` | The longest distance in the ordinated space (like the diagonal in two dimensions) | `dispRity` |
1 | `ellipse.volume`<sup>1</sup> | The volume of the ellipsoid of the space | Donohue _et al._ (2013) |
1 | `mode.val` | The modal value | `dispRity` |
1 | `n.ball.volume` | The hyper-spherical (*n*-ball) volume | `dispRity` |
2 | `pairwise.dist` | The pairwise distances between elements | [`vegan`](https://cran.r-project.org/web/packages/vegan/index.html)`::vegist` |
2 | `radius` | The radius of each dimensions | `dispRity` |
2 | `ranges` | The range of each dimension | `dispRity` |
1 | `span.tree.length` | The minimal spanning tree length | [`vegan`](https://cran.r-project.org/web/packages/vegan/index.html)`::spantree` |
2 | `variances` | The variance of each dimension | `dispRity` |

@@

The convex hull based functions are a call to the `geometry::convhulln` function with the `"FA"` option (computes total area and volume).
Also note that they are really sensitive to the size of the dataset.

@@

The pairwise distances uses the function `vegan::vegdist` and can take the normal `vegdist` options:

@@

Note that this function is a direct call to `vegan::vegdist(matrix, method = method, diag = FALSE, upper = FALSE, ...)`.
